(Re-)bridging the anatomy ontologies with SSSOM

### 2024-05-23 sssomt.tex
Add PURLs to Uberon artefacts.
None of these artefacts are new and therefore do not really belong here
IMO (that gives the impression they are a novelty of this paper, while
they are not, at least not for the bridges and the Composite Metazoan
product; what is new is _how_ we generate them), but reviewer #4 asked
for it.

>>>>

Uberon artefacts concerned by this project are available under the
following permanent URLs:

\begin{tabular}{ll}
\hline
Artefact & PURL\\
\hline
SSSOM mapping set & \url{http://purl.obolibrary.org/obo/uberon/uberon.sssom.tsv}\\
Bridge to ontology \emph{X} & \url{http://purl.obolibrary.org/obo/uberon/bridge/uberon-bridge-to-X.owl}\\
Composite Metazoan & \url{http://purl.obolibrary.org/obo/uberon/composite-metazoan.owl}\\
\hline
\end{tabular}
